---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
--- 


# plus sn10x, SI              
            
            
Baf53cre ENS neurons, SI data               
CR infection 7d, CTL x4  CKO(Ahr-cko) x4                      
       

loading 60k cells,       
cellranger called 35,059 cells           


##### load dependancies                
```{r message=FALSE, warning=FALSE, include=FALSE}
source("I:/Shared_win/projects/RNA_normal/analysis.10x.r")
```   


## load 10x data      

```{r}
filt.10x <- Read10X(data.dir = "../output_plus/filtered_feature_bc_matrix/")
``` 


```{r}
GEX <- filt.10x$`Gene Expression`
FB <- filt.10x$`Antibody Capture`
```


### check datasets   
```{r message=FALSE, warning=FALSE}
dim(GEX)
GEX[1:6,1:6]
```


```{r}
dim(FB)
FB[,1:6]
```


```{r}
rowSums(FB)
```


```{r}
rowSums(FB>0)
```


## FB     
      
```{r}
# build seurat object
FB.seur <- CreateSeuratObject(counts = FB,project = "CR7d_SI")

FB.seur
```


```{r}
rownames(FB.seur)
```

### normalization     
    
perform Seurat 'Demultiplexing with hashtag oligos(HTOs)     
ref https://satijalab.org/seurat/articles/hashing_vignette.html       
    
```{r}
# normalize
FB.seur <- NormalizeData(FB.seur)
FB.seur <- FindVariableFeatures(FB.seur, selection.method = "mean.var.plot")
FB.seur <- ScaleData(FB.seur, features = VariableFeatures(FB.seur))

# independent assay for HTO data  
FB.seur[['HTO']] <- CreateAssayObject(counts = FB)
FB.seur <- NormalizeData(FB.seur, assay = 'HTO', normalization.method = 'CLR')
```


### check demux         

first define FB colors based on conditions                      

```{r eval=FALSE, fig.height=6, fig.width=8.1, include=FALSE}
scales::show_col(ggsci::pal_igv("default")(49))
```


```{r eval=FALSE, fig.height=5, fig.width=5, include=FALSE}
scales::show_col(ggsci::pal_d3("category20b")(20))
scales::show_col(ggsci::pal_d3("category20c")(20))
```


```{r}
color.FB <- ggsci::pal_d3("category20c")(20)[c(1,6,11,16,
                                               2,7,12,17
                                              
                                               )]


level.FB <- c(rownames(FB.seur))

color.FBraw <-  c("#FF6C91","lightgrey",color.FB)
```


```{r}
scales::show_col(color.FBraw, ncol = 6)
scales::show_col(color.FB, ncol = 4)
```


```{r fig.height=6.5, fig.width=12, message=FALSE, warning=FALSE}
par(mfrow=c(2,4))

#plot(sort(rowSums(t(FB))),
#     xlab="reordered cells", 
#     ylab="UMI counts", log="xy",
#     main="sum")


plot(sort(t(FB)[,1]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[1])
plot(sort(t(FB)[,2]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[2])
plot(sort(t(FB)[,3]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[3])
plot(sort(t(FB)[,4]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[4])

plot(sort(t(FB)[,5]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[5])
plot(sort(t(FB)[,6]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[6])
plot(sort(t(FB)[,7]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[7])
plot(sort(t(FB)[,8]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[8])

```


#### range 'q'         

##### q0.50 ~ 0.99       

```{r include=FALSE, paged.print=FALSE}
FB.test <- FB.seur
#cut.list <- list()

table.demux <- data.frame(sample=c("quantile","Doublet",rownames(FB.test),"Negative"))

for(i in 50:99){
  FB.test <- HTODemux(FB.test, assay = "HTO", positive.quantile = i/100)
  table.demux <- cbind(table.demux,
                       c(i/100,table(FB.test$hash.ID)[c("Doublet",rownames(FB.test),"Negative")]))
}
rownames(table.demux) <- table.demux$sample
table.demux <- table.demux[,2:ncol(table.demux)]
table.demux <- data.frame(t(table.demux))
rownames(table.demux) <- NULL
#table.demux
```


```{r paged.print=FALSE}
table.demux
```


```{r fig.width=15, fig.height=10}
#color.FB <- scales::hue_pal()(10)
par(mfrow=c(3,4))


plot(table.demux$Doublet, type="p", col="#FF6C91", pch=16, ylab="Doublet")
plot(table.demux$Negative, type="p", col="lightgrey", pch=16, ylab="Negative")
plot(rowSums(table.demux[,grep("CTL|CKO",colnames(table.demux))]), type="p", col="#306000", pch=16, ylab="Singlet")

#plot(table.demux$quantile, pch=16, ylab="mod-quantile")
plot.new()

plot(table.demux[,2+1], type="p", col=color.FB[1], pch=16, ylab=colnames(table.demux)[2+1])
plot(table.demux[,2+2], type="p", col=color.FB[2], pch=16, ylab=colnames(table.demux)[2+2])
plot(table.demux[,2+3], type="p", col=color.FB[3], pch=16, ylab=colnames(table.demux)[2+3])
plot(table.demux[,2+4], type="p", col=color.FB[4], pch=16, ylab=colnames(table.demux)[2+4])
plot(table.demux[,2+5], type="p", col=color.FB[5], pch=16, ylab=colnames(table.demux)[2+5])
plot(table.demux[,2+6], type="p", col=color.FB[6], pch=16, ylab=colnames(table.demux)[2+6])
plot(table.demux[,2+7], type="p", col=color.FB[7], pch=16, ylab=colnames(table.demux)[2+7])
plot(table.demux[,2+8], type="p", col=color.FB[8], pch=16, ylab=colnames(table.demux)[2+8])

```


##### q0.9900 ~ 0.9999               

```{r include=FALSE, paged.print=FALSE}
FB.test <- FB.seur
#cut.list <- list()

table.demux.s <- data.frame(sample=c("quantile","Doublet",rownames(FB.test),"Negative"))

for(i in 9900:9999){
  FB.test <- HTODemux(FB.test, assay = "HTO", positive.quantile = i/10000)
  table.demux.s <- cbind(table.demux.s,
                       c(i/10000,table(FB.test$hash.ID)[c("Doublet",rownames(FB.test),"Negative")]))
}
rownames(table.demux.s) <- table.demux.s$sample
table.demux.s <- table.demux.s[,2:ncol(table.demux.s)]
table.demux.s <- data.frame(t(table.demux.s))
rownames(table.demux.s) <- NULL
#table.demux.s
```


```{r paged.print=FALSE}
#table.demux.s
```


```{r fig.width=15, fig.height=10}
#color.FB <- scales::hue_pal()(10)
par(mfrow=c(3,4))


plot(table.demux.s$Doublet, type="p", col="#FF6C91", pch=16, ylab="Doublet")
plot(table.demux.s$Negative, type="p", col="lightgrey", pch=16, ylab="Negative")
plot(rowSums(table.demux.s[,grep("CTL|CKO",colnames(table.demux.s))]), type="p", col="#306000", pch=16, ylab="Singlet")

#plot(table.demux.s$quantile, pch=16, ylab="mod-quantile")
plot.new()

plot(table.demux.s[,2+1], type="p", col=color.FB[1], pch=16, ylab=colnames(table.demux.s)[2+1])
plot(table.demux.s[,2+2], type="p", col=color.FB[2], pch=16, ylab=colnames(table.demux.s)[2+2])
plot(table.demux.s[,2+3], type="p", col=color.FB[3], pch=16, ylab=colnames(table.demux.s)[2+3])
plot(table.demux.s[,2+4], type="p", col=color.FB[4], pch=16, ylab=colnames(table.demux.s)[2+4])
plot(table.demux.s[,2+5], type="p", col=color.FB[5], pch=16, ylab=colnames(table.demux.s)[2+5])
plot(table.demux.s[,2+6], type="p", col=color.FB[6], pch=16, ylab=colnames(table.demux.s)[2+6])
plot(table.demux.s[,2+7], type="p", col=color.FB[7], pch=16, ylab=colnames(table.demux.s)[2+7])
plot(table.demux.s[,2+8], type="p", col=color.FB[8], pch=16, ylab=colnames(table.demux.s)[2+8])

```



### demultiplexing       


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.91)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.92)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.93)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.94)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.95)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```

```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.96)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.97)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.98)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.99)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.992)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.994)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.996)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.998)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# seems have to select a much suitable cutoff for CKO.2 based on its counts distribution
# others could check q0.95~q0.99 to choose a better one
# 
# CTL.1  q0.994  242
# CTL.2  q0.99   45
# CTL.3  q0.99   39
# CTL.4  q0.98   74   
# CKO.1  q0.994  136
# CKO.2  UMI 330
# CKO.3  q0.98   224
# CKO.4  q0.95   415
#


cutoff.FB <- c(248,45,39,72,
               156,330,224,430)
names(cutoff.FB) <- rownames(FB.seur)
cutoff.FB
```


```{r fig.height=6.5, fig.width=12, message=FALSE, warning=FALSE}
par(mfrow=c(2,4))

#plot(sort(rowSums(t(FB))),
#     xlab="reordered cells", 
#     ylab="UMI counts", log="xy",
#     main="sum")


plot(sort(t(FB)[,1]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[1])
abline(h=cutoff.FB[1],col = color.FB[1])
plot(sort(t(FB)[,2]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[2])
abline(h=cutoff.FB[2],col = color.FB[2])
plot(sort(t(FB)[,3]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[3])
abline(h=cutoff.FB[3],col = color.FB[3])
plot(sort(t(FB)[,4]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[4])
abline(h=cutoff.FB[4],col = color.FB[4])

plot(sort(t(FB)[,5]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[5])
abline(h=cutoff.FB[5],col = color.FB[5])
plot(sort(t(FB)[,6]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[6])
abline(h=cutoff.FB[6],col = color.FB[6])
plot(sort(t(FB)[,7]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[7])
abline(h=cutoff.FB[7],col = color.FB[7])
plot(sort(t(FB)[,8]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[8])
abline(h=cutoff.FB[8],col = color.FB[8])

```

must process CKO.2 specifically, or the overall result could be messed up         

```{r fig.height=6.5, fig.width=12, message=FALSE, warning=FALSE}
par(mfrow=c(2,4))

#plot(sort(rowSums(t(FB))),
#     xlab="reordered cells", 
#     ylab="UMI counts", log="xy",
#     main="sum")


plot(sort(t(FB)[,1], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[1])
abline(h=cutoff.FB[1],col = color.FB[1])
plot(sort(t(FB)[,2], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[2])
abline(h=cutoff.FB[2],col = color.FB[2])
plot(sort(t(FB)[,3], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[3])
abline(h=cutoff.FB[3],col = color.FB[3])
plot(sort(t(FB)[,4], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[4])
abline(h=cutoff.FB[4],col = color.FB[4])

plot(sort(t(FB)[,5], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[5])
abline(h=cutoff.FB[5],col = color.FB[5])
plot(sort(t(FB)[,6], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[6])
abline(h=cutoff.FB[6],col = color.FB[6])
plot(sort(t(FB)[,7], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[7])
abline(h=cutoff.FB[7],col = color.FB[7])
plot(sort(t(FB)[,8], decreasing = T),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[8])
abline(h=cutoff.FB[8],col = color.FB[8])

```


```{r}
## custom cutoff run this
custom.Demux <- function(FBobj,FBcutoff){
  # define decision matrix
  dd <- FBobj@assays[['HTO']]@counts
  dd <- apply(dd, 2, function(x){
    x > FBcutoff
  })
  x1 <- colSums(dd)
  x1[x1>1] <- "Doublet"
  x1[x1==0] <- "Negative"
  x1[x1==1] <- "Singlet"

  x2 <- x1
  
  bc.slt  <- names(x1)[x1=="Singlet"]
  
  for(bc in bc.slt){
    x2[bc] <- rownames(dd)[dd[,bc]]
  }
  
  FBdf <- data.frame(HTO_classification.global=factor(x1,
                                                      levels = c("Doublet","Negative","Singlet")),
                     hash.ID=factor(x2,
                                    levels = c("Doublet","Negative",rownames(dd))))
  return(FBdf)
}

df.FB <- custom.Demux(FB.seur,cutoff.FB)
```



```{r paged.print=FALSE}
## custom cutoff run this
dim(df.FB)
df.FB[1:10,]
```


```{r}
## custom cutoff run this
table(df.FB)
```

```{r paged.print=FALSE}
## custom cutoff run this
FB.seur@meta.data[,c("HTO_classification.global","hash.ID")] <- df.FB
FB.seur@meta.data[1:4,]
```


```{r}
## default q0.99 run this
#FB.seur$HTO_classification.global <- factor(as.character(FB.seur$HTO_classification.global),
#                                            levels = c("Doublet","Negative","Singlet"))
#FB.seur$hash.ID <- factor(as.character(FB.seur$hash.ID),
#                          levels = c("Doublet","Negative",rownames(FB.seur)))
```


```{r singlelt, fig.height=4, fig.width=4}
sl_stat <- table(FB.seur$HTO_classification.global)
barplot(sl_stat,ylim = c(0,23500),col = c("#FF6C91","lightgrey","#7CAE00"),main = "Feature Barcode statistics")
text(x=1:3*1.2-0.5,y=sl_stat+1280,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
``` 


#### RidgePlot    
##### with ridge plots, raw    
```{r fig.width=12,fig.height=6,message=FALSE, warning=FALSE}
FB.seur@active.ident <- factor(FB.seur$HTO_maxID,levels=rownames(FB.seur))

RidgePlot(FB.seur, assay = 'HTO', features = rownames(FB.seur[['HTO']]),same.y.lims= TRUE, ncol=4,
          cols = color.FB) 
```

##### with ridge plots, filtered    

```{r fig.width=12,fig.height=7,message=FALSE, warning=FALSE}
FB.seur@meta.data$hash.ID.sort <- factor(as.character(FB.seur@meta.data$hash.ID),levels = c("Doublet","Negative",levels(FB.seur@active.ident)))
RidgePlot(FB.seur, assay = 'HTO', features = rownames(FB.seur[['HTO']]), ncol=4,same.y.lims= TRUE,
          cols = c("#FF6C91","lightgrey",color.FB),group.by = "hash.ID.sort") 
```


#### tSNE for HTOs     
     
     
```{r message=FALSE, warning=FALSE}
# first, remove negative cells from th object
#FB.seur.subset <- FB.seur

# Calculate a tSNE embedding of the HTO data
#DefaultAssay(FB.seur.subset) <- "HTO"

#FB.seur.subset <- ScaleData(FB.seur.subset, features = rownames(FB.seur.subset), verbose = FALSE)
##FB.seur.subset <- RunPCA(FB.seur.subset, features = rownames(FB.seur.subset), approx = FALSE)
##FB.seur.subset <- RunTSNE(FB.seur.subset, dims = 1:8, perplexity = 500, check_duplicates = FALSE)

#FB.seur.subset <- RunPCA(FB.seur.subset, features = setdiff(rownames(FB.seur.subset),"CKO.2"), approx = FALSE)
#FB.seur.subset <- RunTSNE(FB.seur.subset, dims = 1:7, perplexity = 300, check_duplicates = FALSE)

#saveRDS(FB.seur.subset, "FB1222.seur.subset.rds")
FB.seur.subset <- readRDS("FB1222.seur.subset.rds")


```


```{r fig.width=5.5,fig.height=8.6}
multiplot(
DimPlot(FB.seur.subset, order = rev(levels(FB.seur@active.ident)),
        cols = color.FB) + labs(title = "FB Max_ID"), 
DimPlot(FB.seur.subset, order = c("Doublet",rev(levels(FB.seur@active.ident)),"Negative"), group.by = 'hash.ID', label = F,
        cols = c("lightgrey",color.FB,"#FF6C91")) + 
  labs(title = "FB Filtered_ID") + theme(plot.title = element_text(hjust = 0)) ,
cols = 1)
```


### stat    

```{r}
FB.seur$HTO_classification.global <- factor(as.character(FB.seur$HTO_classification.global),
                                            levels = c("Doublet","Negative","Singlet"))
Idents(FB.seur) <- "HTO_classification.global"
VlnPlot(FB.seur, features = "nCount_RNA", pt.size = 0, log = TRUE, cols = c("#F8766D","lightgrey","#00BA38"))
VlnPlot(FB.seur, features = "nCount_RNA", pt.size = 0, log = TRUE, cols = c("#F8766D","lightgrey","#00BA38")) + geom_jitter(alpha=0.015)
```



```{r}
table(FB.seur@meta.data$hash.ID.sort)
```

```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(FB.seur$hash.ID.sort)
barplot(sl_stat,ylim = c(0,12800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:10*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID.sort), las=3, cex.axis=0.85)
text(x=1:10*1.2-0.45,y=sl_stat+875,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


## GEX    
    
mainly follow https://satijalab.org/seurat/articles/pbmc3k_tutorial.html    


```{r message=FALSE, warning=FALSE}
GEX.seur <- CreateSeuratObject(counts = GEX,
                               min.cells = 3,
                               min.features = 200,
                               project = "CR7d_SI")
GEX.seur
```


### filtering    

#### MT genes   
```{r}
grep("^mt-",rownames(GEX),value = T)
```


```{r}
MT_gene <- grep("^mt-",rownames(GEX.seur),value = T)
GEX.seur[["percent.mt"]] <- PercentageFeatureSet(GEX.seur, features = MT_gene)

RB_gene <- grep("^Rps|^Rpl",rownames(GEX.seur),value = T)
GEX.seur[["percent.rb"]] <- PercentageFeatureSet(GEX.seur, features = RB_gene)

# Visualize QC metrics as a violin plot
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.01)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb")
plota + plotb + plotc
```

#### add FB info      

```{r}
GEX.seur$FB.info <- FB.seur@meta.data[rownames(GEX.seur@meta.data),"hash.ID"]
#head(GEX.seur@meta.data)
```


```{r}
table(GEX.seur$FB.info)
```


```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0, split.by = "FB.info")
```




```{r}
GEX.seur <- subset(GEX.seur, subset = FB.info!="Doublet" & FB.info!="Negative" & FB.info!="CKO.2")
GEX.seur
```


```{r fig.width=8, fig.height=5}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.1)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```


```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0, split.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb") 
plota + plotb + plotc
```

#### filtering        


```{r}
GEX.seur <- subset(GEX.seur, subset = percent.mt < 5 & nFeature_RNA > 500 & nFeature_RNA < 4000 & nCount_RNA < 10000)
GEX.seur
```



filtered obj        
```{r fig.width=8, fig.height=5}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.1)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FBraw,
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FBraw,
        pt.size = 0, split.by = "FB.info")
```

```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb") 
plota + plotb + plotc
```

```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(FB.seur$hash.ID.sort)
barplot(sl_stat,ylim = c(0,10800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:10*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID.sort), las=3, cex.axis=0.85)
text(x=1:10*1.2-0.45,y=sl_stat+675,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(GEX.seur$FB.info)
barplot(sl_stat,ylim = c(0,6800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:10*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID.sort), las=3, cex.axis=0.85)
text(x=1:10*1.2-0.45,y=sl_stat+475,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


#### check cellcycle       
```{r}
s.genes <- Hmisc::capitalize(tolower(cc.genes.updated.2019$s.genes))
g2m.genes <- Hmisc::capitalize(tolower(cc.genes.updated.2019$g2m.genes))

GEX.seur <- CellCycleScoring(GEX.seur,
                             s.features = s.genes,
                             g2m.features = g2m.genes)
```

```{r}
VlnPlot(GEX.seur, features = c("S.Score", "G2M.Score"), group.by = "FB.info", 
    ncol = 2, pt.size = 0.1)
```

```{r message=FALSE, warning=FALSE}
GEX.seur.cc <- GEX.seur

GEX.seur.cc <- NormalizeData(GEX.seur.cc)
GEX.seur.cc <- FindVariableFeatures(GEX.seur.cc)
GEX.seur.cc <- ScaleData(GEX.seur.cc)
Idents(GEX.seur.cc) <- "Phase"
RidgePlot(GEX.seur.cc, features = c("Pcna", "Top2a", "Mcm6", "Mki67"), ncol = 2)
```

```{r message=FALSE, warning=FALSE}
GEX.seur.cc <- RunPCA(GEX.seur.cc, features = c(s.genes, g2m.genes))
DimPlot(GEX.seur.cc, reduction = 'pca')
```


##### no cycling !          


### Markers and Clusters            

#### Normalizing          

```{r}
GEX.seur <- NormalizeData(GEX.seur, normalization.method = "LogNormalize", scale.factor = 10000)
```


```{r message=FALSE, warning=FALSE,fig.width=12,fig.height=5}
GEX.seur <- FindVariableFeatures(GEX.seur, selection.method = "vst", nfeatures = 1500)

# Identify the 10 most highly variable genes
#top10 <- head(VariableFeatures(GEX.seur), 10)
top20 <- head(VariableFeatures(GEX.seur), 20)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(GEX.seur)
plot2 <- LabelPoints(plot = plot1, points = top20, repel = T)
plot1 + plot2
```


```{r}
head(VariableFeatures(GEX.seur), 200)
```


```{r}
GEX.seur <- ScaleData(GEX.seur, features = rownames(GEX.seur))
```


#### PCA       

```{r}
# exclude MT genes  and more 

#DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AY|^Gm|^Hist",rownames(GEX.seur),value = T)

DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|Mzb1|Vpreb|Lars2|Jun|Fos|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AY|^AC|^AA|^AW|^BC|^Gm|^Hist|Rik$|-ps",
            rownames(GEX.seur),value = T)
CC_gene <- Hmisc::capitalize(tolower(as.vector(unlist(cc.genes.updated.2019))))


VariableFeatures(GEX.seur) <- setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,
                                                  DIG, 
                                                  CC_gene) )

GEX.seur <- RunPCA(GEX.seur, features = VariableFeatures(GEX.seur))
```


```{r}
length(setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,DIG,CC_gene)))
setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,DIG,CC_gene))[1:300]
```


```{r fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "orig.ident") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "orig.ident")
```


```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "FB.info", cols = color.FB) +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "FB.info", cols = color.FB)
```


```{r pcsheat,fig.width=12,fig.height=15}
DimHeatmap(GEX.seur, dims = 1:12, cells = 1500, balanced = TRUE,ncol = 4)
```


##### decide PCs to use          
     
```{r}
ElbowPlot(GEX.seur,ndims = 50)
```

```{r}
PCs <- 1:25
GEX.seur <- FindNeighbors(GEX.seur, dims = PCs, k.param = 20)
GEX.seur <- FindClusters(GEX.seur, method = 'igraph' ,resolution = 2)
```


#### Run UMAP/tSNE    

```{r}
GEX.seur <- RunTSNE(GEX.seur, dims=PCs, complexity = 100)
GEX.seur <- RunUMAP(GEX.seur, dims=PCs, n.neighbors = 20, seed.use = 145)
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "tsne", label = T) + DimPlot(GEX.seur, reduction = "umap", label = T)
```



```{r fig.width=7.5,fig.height=6}
FeaturePlot(GEX.seur, reduction = "umap", features = c("nFeature_RNA","nCount_RNA","percent.mt","percent.rb"))
```


```{r  fig.width=12.5, fig.height=6.4}
DimPlot(GEX.seur, label = F, pt.size = 0.05, repel = F, reduction = 'umap', group.by = "FB.info", split.by = "FB.info", 
        ncol = 4, cols = color.FB)
#DimPlot(GEX.seur, label = F, pt.size = 0.05, repel = F, reduction = 'umap', group.by = "FB.info", split.by = "FB.info", 
#        ncol = 3, cols = color.FB)
``` 


```{r}
GEX.seur$cnt <- factor(gsub(".1$|.2$|.3$|.4$","",as.character(GEX.seur$FB.info)),
                       levels = c("CTL",
                                  "CKO"))
color.cnt <- color.FB[c(1,5)]
```


```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "cnt", cols = color.cnt)
```

#### check short markers          

```{r fig.height=6.5, fig.width=13.5}
markers.new.s <- list(EMN=c("Chat","Bnc2","Tox","Ptprt",
                       "Gfra2","Oprk1","Adamtsl1", 
                       "Fbxw15","Fbxw24","Chrna7",
                       "Satb1","Cntnap5b",
                       "Gabrb1","Nxph1","Lama2","Lrrc7",
                       "Ryr3","Eda","Tac1",
                       "Kctd8","Ntrk2","Penk",
                       "Fut9","Nfatc1","Egfr","Mgll",
                       "Chrm3"
                       ),
                 IMN=c("Nos1","Kcnab1",
                       "Gfra1","Etv1",
                       "Man1a","Airn",
                       "Adcy2","Cmah","Creb5","Vip","Pde1a",
                       "Ebf1","Gpc5"
                       ),
                 IN=c("Npas3","Synpr","St18","Gal",
                      "Kcnk13",
                      "Neurod6","Moxd1","Sctr",
                      "Piezo1","Sst","Adamts9","Kcnn2",
                      "Calb2"),
                 IPAN=c("Calcb","Nmu","Adgrg6","Pcdh10",
                        "Ngfr","Galr1","Il7","Aff2",
                        "Gpr149","Cdh6","Cdh8",
                        "Clstn2","Ano2","Ntrk3",
                        "Cpne4","Vwc2l","Cdh9","Scgn",
                        "Vcan","Cck","Piezo2","Kcnh7",
                        "Rerg","Bmpr1b","Skap1","Ntng1",
                        "Tafa2","Nxph2"),
                 CONTAM=c("Actl6b","Phox2b","Sox10","Plp1",
                          "Gfap","Rxrg","Pdgfra","Acta2"))


pm.CL_new.s <- DotPlot(subset(GEX.seur,subset=cnt %in% c("CTL")), features = as.vector(unlist(markers.new.s)), group.by = "seurat_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="CTL only")
pm.CL_new.s

pm.All_new.s <- DotPlot(GEX.seur, features = as.vector(unlist(markers.new.s)), group.by = "seurat_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="All")
pm.All_new.s
```


#### DoubletFinder       

```{r}
library(DoubletFinder)
```

```{r include=FALSE}
# to find a better pk
sweep.res.list <- paramSweep_v3(GEX.seur, PCs = PCs, sct = FALSE) 
```

```{r message=FALSE, warning=FALSE}
for(i in 1:length(sweep.res.list)){
  if(length(sweep.res.list[[i]]$pANN[is.nan(sweep.res.list[[i]]$pANN)]) !=0){
    if(i!=1){
      sweep.res.list[[i]] <- sweep.res.list[[i-1]]
    }else(
      sweep.res.list[[i]] <- sweep.res.list[[i+1]]
    )
  }
}
sweep.stats <- summarizeSweep(sweep.res.list, GT=FALSE)
bcmvn <- find.pK(sweep.stats)
```

```{r}
pk_v <- as.numeric(as.character(bcmvn$pK))
pk_good <- pk_v[bcmvn$BCmetric==max(bcmvn$BCmetric)]
```

```{r}
# specify expected doublet number     
nExp_poi <- round(0.05*length(colnames(GEX.seur)))

GEX.seur <- doubletFinder_v3(GEX.seur, PCs = PCs, pN = 0.25, pK = pk_good, 
                             nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
colnames(GEX.seur@meta.data)[ncol(GEX.seur@meta.data)] <- "DoubletFinder0.05"
```

```{r message=FALSE, warning=FALSE}
# specify expected doublet number     
nExp_poi <- round(0.1*length(colnames(GEX.seur)))

GEX.seur <- doubletFinder_v3(GEX.seur, PCs = PCs, pN = 0.25, pK = pk_good, 
                             nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
colnames(GEX.seur@meta.data)[ncol(GEX.seur@meta.data)] <- "DoubletFinder0.1"
```


```{r fig.width=10.8,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.05") +
  DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.1")
```



#### sort_clusters            


```{r}
GEX.seur$sort_clusters <- factor(as.character(GEX.seur$seurat_clusters),
                                 levels = c(0,3,4,14,10,8,1,17,28,     # EMN
                                            5,2,6,7,13,16,26,     # IMN
                                            9,20, 22,     # IN
                                            15,11, 12,21, 29,19,32,     # IPAN
                                            27,25,18,31,24,     # Mix
                                            30,     # Glia
                                            23      # SMC
                                            ))

# preAnno1
GEX.seur$preAnno1 <- as.character(GEX.seur$seurat_clusters)

GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(0,4,3,14,10,8,1,17,28)] <- "EMN"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(5,2,6,7,13,16,26)] <- "IMN"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(9,20, 22)] <- "IN"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(15,11, 12,21, 29,32,19)] <- "IPAN"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(27,25,30,18,31,24)] <- "MIX"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(30)] <- "Glia"
GEX.seur$preAnno1[GEX.seur$preAnno1 %in% c(23)] <- "SMC"

GEX.seur$preAnno1 <- factor(GEX.seur$preAnno1,
                            levels = c("EMN","IMN","IN","IPAN",
                                       "MIX","Glia","SMC"))
# preAnno2
GEX.seur$preAnno2 <- as.character(GEX.seur$seurat_clusters)

GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(0,4,3,14)] <- "EMN1"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(10)] <- "EMN2"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(8,1)] <- "EMN3"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(17,28)] <- "EMN4"

GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(5,2,6,7)] <- "IMN1"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(13)] <- "IMN2"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(16)] <- "IMN3"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(26)] <- "IMN4"

GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(9)] <- "IN1"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(20)] <- "IN2"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(22)] <- "IN3"

GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(15,11)] <- "IPAN1"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(12,21)] <- "IPAN2"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(29,32)] <- "IPAN3"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(19)] <- "IPAN4"

GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(27,25,30,18,31,24)] <- "MIX"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(30)] <- "Glia"
GEX.seur$preAnno2[GEX.seur$preAnno2 %in% c(23)] <- "SMC"

GEX.seur$preAnno2 <- factor(GEX.seur$preAnno2,
                            levels = c(paste0("EMN",1:4),
                                       paste0("IMN",1:4),
                                       paste0("IN",1:3),
                                       paste0("IPAN",1:4),
                                       "MIX","Glia","SMC"))


```



```{r fig.height=6.5, fig.width=12.5}
pm.CL_new.s <- DotPlot(subset(GEX.seur,subset=cnt %in% c("CTL")), features = as.vector(unlist(markers.new.s)), group.by = "sort_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="CL only")
pm.CL_new.s

pm.All_new.s <- DotPlot(GEX.seur, features = as.vector(unlist(markers.new.s)), group.by = "sort_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="All")
pm.All_new.s
```


```{r fig.height=5, fig.width=12.5}
pm.CL_new.s <- DotPlot(subset(GEX.seur,subset=cnt %in% c("CTL")), features = as.vector(unlist(markers.new.s)), group.by = "preAnno2",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="CL only")
pm.CL_new.s

pm.All_new.s <- DotPlot(GEX.seur, features = as.vector(unlist(markers.new.s)), group.by = "preAnno2",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="All")
pm.All_new.s
```

```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "preAnno2") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "cnt", cols = color.cnt)
```

```{r}
#saveRDS(GEX.seur,"GEX0112.seur.pre.rds")
```


## pure                


```{r}
GEX.pure <- subset(GEX.seur, subset = preAnno1 %in% levels(GEX.seur$preAnno1)[1:4] & DoubletFinder0.1 == "Singlet")
GEX.pure
```


```{r fig.height=5, fig.width=12.5}
pm.CL_new.s <- DotPlot(subset(GEX.pure,subset=cnt %in% c("CTL")), features = as.vector(unlist(markers.new.s)), group.by = "preAnno2",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="CL only")
pm.CL_new.s

pm.All_new.s <- DotPlot(GEX.pure, features = as.vector(unlist(markers.new.s)), group.by = "preAnno2",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1,size = 9.15))+ scale_y_discrete(limits=rev) + labs(title="All")
pm.All_new.s
```

```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.pure, reduction = "umap", label = T, group.by = "preAnno2") +
  DimPlot(GEX.pure, reduction = "umap", label = F, group.by = "cnt", cols = color.cnt)
```


## cell composition                       

### heatmap          

```{r fig.width=7.2, fig.height=4}
cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.pure$FB.info,
      clusters=GEX.pure$preAnno2)[c(3:7,9,10),c(1:15)],
                   main = "Cell Count",
                   gaps_row = c(4),
      gaps_col = c(4,8,11,15),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.pure$FB.info,
                                clusters=GEX.pure$preAnno2)[c(3:7,9,10),c(1:15)]),
                   main = "Cell Ratio",
                   gaps_row = c(4),
      gaps_col = c(4,8,11,15),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 1)
```


### barplot       

```{r}
GEX.pure$rep <- paste0("rep",
                        gsub("CTL|CKO","",as.character(GEX.pure$FB.info)))
```


```{r}
stat_preAnno2 <- GEX.pure@meta.data[,c("cnt","rep","preAnno2")]

stat_preAnno2.s <- stat_preAnno2 %>%
  group_by(cnt,rep,preAnno2) %>%
  summarise(count=n()) %>%
  mutate(prop= count/sum(count)) %>%
  ungroup
```


```{r  fig.height=3.5, fig.width=8.5}
pcom.preAnno2 <- stat_preAnno2.s %>%
  ggplot(aes(x = preAnno2, y = 100*prop, color=cnt)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  theme_classic(base_size = 15) +
  scale_color_manual(values = c("skyblue","pink"), name="") +
  labs(title="Cell Composition of SI data, preAnno2", y = "Proportion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6)) +
  
  geom_point(aes(x=preAnno2, y = 100*prop, color= cnt),
             position = position_dodge(0.75),
             shape=16,alpha=0.75,size=2.15,
             stroke=0.15, show.legend=F)

pcom.preAnno2
```

#### sig.test          

glm.nb - anova.LRT           


```{r message=FALSE, warning=FALSE}

Sort.N <- c("CTL","CKO")

glm.nb_anova.preAnno2 <- list()

for(x1 in 1:2){
  for(x2 in 1:2){
    if(x2>x1){
      
      stat_preAnno2.s_N <- stat_preAnno2.s %>% filter(cnt %in% c(Sort.N[x1],Sort.N[x2]))
      
      total.N <- stat_preAnno2.s_N %>%
        group_by(cnt, rep) %>%
        summarise(total=sum(count)) %>% ungroup() %>% as.data.frame()
      
      rownames(total.N) <- paste0(as.character(total.N$cnt),
                                  "_",
                                  as.character(total.N$rep))
      
      stat_preAnno2.s_N$total <- total.N[paste0(stat_preAnno2.s_N$cnt,
                                            "_",
                                            stat_preAnno2.s_N$rep),"total"]
      
      glm.nb_anova.preAnno2[[paste0(Sort.N[x1],"vs",Sort.N[x2])]] <- list()
      
      for(AA in levels(stat_preAnno2.s_N$preAnno2)){
        glm.nb_anova.preAnno2[[paste0(Sort.N[x1],"vs",Sort.N[x2])]][[AA]] <- tryCatch({
          aaa <- stat_preAnno2.s_N %>% filter(preAnno2==AA)
          aaa.glmnb <- MASS::glm.nb(count ~ cnt + offset(log(total)), data = aaa, maxit=1000)
          aaa.anova <- anova(aaa.glmnb, test = "LRT")
          aaa.anova$'Pr(>Chi)'[2]
        }, error=function(e){
        
          tryCatch({
            aaa <- stat_preAnno2.s_N %>% filter(preAnno2==AA)
            aaa.glmnb <- MASS::glm.nb(count ~ cnt + offset(log(total)), data = aaa, maxit=100)
            aaa.anova <- anova(aaa.glmnb, test = "LRT")
            aaa.anova$'Pr(>Chi)'[2]
          }, error=function(e){
            
            tryCatch({
              aaa <- stat_preAnno2.s_N %>% filter(preAnno2==AA)
              aaa.glmnb <- MASS::glm.nb(count ~ cnt + offset(log(total)), data = aaa, maxit=10)
              aaa.anova <- anova(aaa.glmnb, test = "LRT")
              aaa.anova$'Pr(>Chi)'[2]
            }, error = function(e){
              NA
            })     
          })
        })
      }
      glm.nb_anova.preAnno2[[paste0(Sort.N[x1],"vs",Sort.N[x2])]] <- unlist(glm.nb_anova.preAnno2[[paste0(Sort.N[x1],"vs",Sort.N[x2])]]) 
    }
  }
}


```


```{r}
glm.nb_anova.preAnno2_df <- t(data.frame(Reduce(function(x,y){rbind(x,y)},glm.nb_anova.preAnno2)))
rownames(glm.nb_anova.preAnno2_df) <- names(glm.nb_anova.preAnno2)
colnames(glm.nb_anova.preAnno2_df) <- gsub("X","C",colnames(glm.nb_anova.preAnno2_df))
glm.nb_anova.preAnno2_df
```







